{\itshape The geography of urban boundaries in Great Britain from the network of Twitter user spatial interactions}

### 2016-05-01 urban_boundaries_gb_IJGIS/IJGIS/Paper.tex
new figure
new
edits

\title{{\itshape Delineate urban boundaries in Great Britain from the network of Twitter user spatial interactions} }
\maketitle

@@

\begin{figure}[ht]
\begin{center}
\includegraphics[width=0.8\linewidth]{./figure/S2_twitter_density_Fig_1}
\caption{\bfseries{A density map of the Twitter user locations for July 2014}}
\label{S2_Fig}
\end{center}
\end{figure}

>>>>

\title{{\itshape The geography of urban boundaries in Great Britain from the network of Twitter user spatial interactions} }
\maketitle

@@

\begin{figure}[ht]
\begin{center}
\includegraphics[width=0.8\linewidth]{./figure/usa}
\caption{\bfseries{Each point corresponds to a geo-located tweet collected for this study. Twitter activity is most apparent in urban areas.}}
\label{S2_Fig}
\end{center}
\end{figure}
